---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%",
  fig.width = 6, 
  fig.height = 3,
  dpi = 300
)
```
# Representing harmony with the hrep package

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/pmcharrison/hrep.svg?branch=master)](https://travis-ci.org/pmcharrison/hrep)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pmcharrison/hrep?branch=master&svg=true)](https://ci.appveyor.com/project/pmcharrison/hrep)
[![Coverage status](https://coveralls.io/repos/github/pmcharrison/hrep/badge.svg)](https://coveralls.io/r/pmcharrison/hrep?branch=master)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2545770.svg)](https://doi.org/10.5281/zenodo.2545770)

The *hrep* R package provides utilities for representing and manipulating 
chord sequences for perceptually informed harmony modelling.
The available representations include symbolic representations,
acoustic representations, and sensory representations.
Integer encodings are defined for several symbolic representations,
allowing the user to efficiently express chord sequences as sequences
of integers.

## Resources

- [Function-level documentation](https://pmcharrison.github.io/hrep/reference/index.html)
- [Changelog](https://pmcharrison.github.io/hrep/news/index.html)
- [File an issue](https://github.com/pmcharrison/hrep/issues)
- [Music corpora](https://github.com/pmcharrison/hcorp)
- [Models of simultaneous consonance](https://github.com/pmcharrison/incon)
- [Automatic voicing of chord sequences](https://github.com/pmcharrison/voicer)

## Installation

The *hrep* package may be installed from GitHub as follows:

``` r
if (!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("pmcharrison/hrep")
```

## Example usage

Chords may be defined as sequences of integers, with each integer
corresponding to a pitch or a pitch class.
The following chord defines a C major triad in first inversion:

```{r}
library(hrep)
x <- pi_chord(c(52, 60, 67))
print(x)
```

From this symbolic representation, it is possible to derive various 
acoustic and sensory representations, such as:

a) A wave:

```{r}
plot(wave(x))
```

b) A sparse pitch spectrum:

```{r}
plot(sparse_pi_spectrum(x))
```

c) A sparse pitch-class spectrum:

```{r}
plot(sparse_pc_spectrum(x))
```

d) A smooth pitch-class spectrum:

```{r}
plot(smooth_pc_spectrum(x))
```

Chords can be translated to various symbolic representations,
which can be encoded to integer formats.
For example, here we convert the chord to the pitch-class chord representation,
and then encode it to an integer.

```{r}
pc_chord((x))
as.integer(encode(pc_chord(x)))
```

Similarly, the following code expresses the chord as a pitch-class set,
and then encodes the pitch-class set as an integer.

```{r}
pc_set(x)
as.integer(encode(pc_set(x)))
```
